Fractional Types

### 2013-02-23 frac.tex
cleaned up examples in 4.4

\begin{example}
Consider the combinator {{c : bool * 1 <-> bool * 1}}, with {{c = id}}.

\noindent Using {{trace*}}, we construct the
combinator {{trace* c : 1 <-> 1}}. Applying this to 
{{() : 1}} requires us to find a value {{b : bool}} such that 
{{(b,()) ~~d~~ (b,())}}. Given that the type {{bool}} 
has two values, there are two values {{false}} and {{true}} that satisfy the 
constraint. In other words, {{() ~~(trace* c)~~() }}.
\end{example}

\begin{example}
\label{ch3:ex:annihilate}
Consider a small variation on the combinator {{c}} above:

{{c : bool * 1 <-> bool * 1}}

{{c = swap+ (*) id }}

\noindent which negates the boolean component of its incoming
pair. Using the multiplicative trace operator, we can construct the
combinator {{trace* c : 1 <-> 1}} as before. But now, applying this
combinator to {{() : 1}} requires us to find a value {{b : bool}} such
that {{(b,()) ~~swap+~~ (b,())}} which is impossible since {{swap+}} 
has no fixed points.  Operationally, the evaluation of
such a combinator should produce no value (were it to even terminate).
\end{example}

>>>>

Consider the combinator {{id : bool * 1 <-> bool * 1}}.
Using {{trace*}}, we construct the combinator {{trace* c : 1 <-> 1}}.
Applying this to {{() : 1}} requires us to find a value {{b : bool}} such
that {{(b,()) ~~d~~ (b,())}}. Given that the type {{bool}} has two values,
there are two values {{false}} and {{true}} that satisfy the constraint.
In other words, {{()~~(trace* id)~~() }}.

%% \label{ch3:ex:annihilate}
Consider another combinator that also has the type {{bool * 1 <-. bool * 1}},
but is instead defined to be {{c = swap+ (*) id }}, which negates the boolean
component of its incoming
pair. Using the multiplicative trace operator, we can construct the
combinator {{trace* c : 1 <-> 1}} as before. But now, applying this
combinator to {{() : 1}} requires us to find a value {{b : bool}} such
that {{(b,()) ~~swap+ (*) id~~ (b,())}} which is impossible since {{swap+}} 
has no fixed points.  Operationally, the evaluation of
such a combinator should produce no value (were it to even terminate).
